Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-01-20 R0V0.tex
Continue writing the components of W for the new example.
Finish typing the metric. Start the "new formulation" of the main result.
Propagate changes of the set Xi along the examples

\mypara Following the notation introduced in \cite{Tanaka2011}, for each index $i\in\mathbb{N}_{[1,N]}$, define the set 
\begin{subequations}
	\begin{align*}
		\Xi=\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ |\mathbin{\mathtt{col}}(Y,j)\in\mathbf{C}_j,\\
		\arg(Y_{ij}(\cdot,u))\in\mathbf{X}(\mathscr{K}(k)),\forall i\in\mathbb{N}_{[1,m]},\forall j\in\mathbb{N}_{[1,n]},k\in\mathbb{N}_{[1,N]}\}\;,
	\end{align*}
\end{subequations}
where $\mathbin{\mathtt{col}}(Y,j)$ stands for the $j$-th column of the matrix $Y$, the set $\mathbf{C}_j$ is the space spanned by the sparsity vector $v_j\in\mathbb{R}^{n}$, and the set $\mathbf{X}(\mathscr{K}(k))$ is the space spanned by components of $x$ indexed by the set $\mathscr{K}(k)$.

\mypara The set $\Xi$ defines the topology of the differential feedback law to be designed for system~\eqref{eq:general system:differential} and the dependence of each element of the matrix $Y$ on the state-space variables. Note that, whenever system \eqref{eq:general system} is linear, the set $\mathbf{X}_i$ is empty, for all indexes $i\in\mathbb{N}_{[1,N]}$, and $\Xi$ reduces to the set $\mathcal{K}$ defined in \cite{Tanaka2011}.

\begin{theorem}\label{thm:main result}
	If there exists a sum-separable control-contraction metric for system \eqref{eq:general system}, then there exists a solution to Problem~\ref{problem formulation}.
\end{theorem}

@@

\mypara In the ``neighbor'' case, the constraint imposed on the matrix $Y$ was that each line of this matrix should depend on the system $i$ and on its neighbors. The the set $\mathscr{K}$ is defined, for each index $i=2,3$, as $\mathscr{K}(i)=\{i-1,i,i+1\}$, $\mathscr{K}(1)=\{1,2\}$ and $\mathscr{K}(4)=\{3,4\}$. The sets $\mathbf{C}_j$, $j\in\mathbb{N}_{[1,8]}$, are defined as
\begin{equation*}
	\begin{array}{rl}
		\mathbf{C}_1=\mathbf{C}_2=\left\{\begin{bmatrix}1, 1, 0, 0\end{bmatrix}^\top\right\},&\mathbf{C}_3=\mathbf{C}_4=\left\{\begin{bmatrix}1, 1, 1, 0\end{bmatrix}^\top\right\},\\
		\mathbf{C}_5=\mathbf{C}_6=\left\{\begin{bmatrix}0, 1, 1, 1\end{bmatrix}^\top\right\},&		    \mathbf{C}_7=\mathbf{C}_8=\left\{\begin{bmatrix}0, 0, 1, 1\end{bmatrix}^\top\right\}\;.
	\end{array} 
\end{equation*}

\mypara The sets $\mathbf{X}(\mathscr{K}(\cdot))$ are defined as $\mathbf{X}(\mathscr{K}(1))=\{q_1,q_2\}$,  $\mathbf{X}(\mathscr{K}(2))=\{q_1,q_2,q_3\}$, $\mathbf{X}(\mathscr{K}(3))=\{q_2,q_3,q_4\}$ and $\mathbf{X}(\mathscr{K}(4))=\{q_3,q_4\}$.

\mypara The time taken by the parser to solve the MI \eqref{eq:MI formulation}, in this case, was 3.5 seconds. The matrix $W$ is given by
\begin{equation*}
		W=\mathbin{\mathtt{diag}}(2,1,1,1,1,1,2,1)
\end{equation*}
and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:neighbor} with elements
\begin{align*}
	Y_{12}(q_1,\breve{q}_1)=&-2.5(1+\sum_{j=1}^2x_j^2+y_j^2)\;,\\	
	Y_{24}(q_2,\breve{q}_2)=&-2.3(1+\sum_{j=1}^3x_j^2+y_j^2)\;,\\	
	Y_{36}(q_3,\breve{q}_3)=&-2.2(1+\sum_{j=2}^4x_j^2+y_j^2)\;,\\	
	Y_{48}(q_4,\breve{q}_4)=&-1.7(1+\sum_{j=3}^4x_j^2+y_j^2)\;.\\	
\end{align*}

\begin{figure*}
\begin{equation}\label{eq:example:Y:neighbor}
	Y(q)=\begin{bmatrix}
	-1.8y_1,&Y_{12}(q_1,\breve{q}_1),&0,&0,&0,&0,&0,&0\\
	0,&0,&-2y_2,&Y_{24}(q_2,\breve{q}_2),&0,&0,&0,&0\\
	0,&0,&0,&0,&-2y_3,&Y_{36}(q_3,\breve{q}_3),&0,&0\\
	0,&0,&0,&0,&0,&0,&-2y_4,&Y_{48}(q_4,\breve{q}_4)
	\end{bmatrix}
\end{equation}
\end{figure*}

\mypara In the last case, the fully decentralized scenario has been considered. The time taken by the parser to solve the MI~\eqref{eq:MI formulation} was 2.6 seconds. In this case, $\mathscr{K}(k)=\{k\}$ and $\mathbf{X}(\mathscr{K}(k))=\{q_k\}$, where $k\in\mathbb{N}_{[1,4]}$. Moreover, 
\begin{equation*}
	\begin{array}{rl}
		\mathbf{C}_1=\mathbf{C}_2=\left\{\begin{bmatrix}1,0,0,0\end{bmatrix}^\top\right\},&\mathbf{C}_3=\mathbf{C}_4=\left\{\begin{bmatrix}0,1,0,0\end{bmatrix}^\top\right\},\\
		\mathbf{C}_5=\mathbf{C}_6=\left\{\begin{bmatrix}0,0,1,0\end{bmatrix}^\top\right\},&\mathbf{C}_7=\mathbf{C}_8=\left\{\begin{bmatrix}0,0,0,1\end{bmatrix}^\top\right\}\;.
	\end{array}
\end{equation*}
Solving the MI \eqref{eq:MI formulation} the following matrices $W$ and $Y$ were obtained
\begin{align*}
 W=&\mathbin{\mathtt{diag}}\left(2,1,1,1,1,1,1,1\right),\\
 Y(q)=&\begin{bmatrix}
 	\overline{Y}(q_1)&0&0&0\\
 	0&\overline{Y}(q_2)&0&0\\
 	0&0&\overline{Y}(q_3)&0\\
 	0&0&0&\overline{Y}(q_4)
 \end{bmatrix}
\end{align*}
where
\begin{align*}
 \overline{Y}(q_i)=-\begin{bmatrix}2y_i,3+2(x_i^2+y_i^2)\end{bmatrix}
\end{align*}

@@

\mypara In the unconstrained case, the solver took 9.8s to solve the MI~\eqref{eq:MI formulation} using chordal graphs. The matrix $W$ is given by $\mathbin{\mathtt{diag}}(\overline{W},\overline{W},\overline{W},\overline{W})$, where $\overline{W}=\mathbin{\mathtt{diag}}(0.69,1.24)$. The matrix $Y$ is given by
\begin{equation*}
	Y(q)=\begin{bmatrix}
	\overline{Y}_1(q)&0_{2\times1}&0_{2\times1}&0_{2\times1}\\
	0_{2\times1}&\overline{Y}_2(q)&0_{2\times1}&0_{2\times1}\\
	0_{2\times1}&0_{2\times1}&\overline{Y}_3(q)&0_{2\times1}\\
	0_{2\times1}&0_{2\times1}&0_{2\times1}&\overline{Y}_4(q)
	\end{bmatrix}\;,
\end{equation*}
where $\overline{Y}_i(q)=-\begin{bmatrix}2.38y_i,&2.88+\sum_{j=1}^4(x_j^2+y_j^2)\end{bmatrix}$

>>>>

\mypara Following the notation introduced in \cite{Tanaka2011}, for each index $i\in\mathbb{N}_{[1,N]}$, define the set 
\begin{align}
		\Xi=&\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ |Y_{pq}:\mathtt{proj}_{\mathscr{K}(i)}(\mathbb{R}^n)\to\mathbb{R},\nonumber\\
		&\mathbin{\mathtt{row}}(Y,p)\in\mathbf{C}(i),\forall p\in\mathbb{N}_{[1,m]},\forall q\in\mathbb{N}_{[1,n]},\nonumber\\
		&i\in\mathbb{N}_{[1,N]}\}\;,
\end{align}
where $Y_{pq}$ is the component of $Y$ located at row $p$ and column $q$, the notation $\mathtt{proj}_{\mathscr{K}(i)}(\mathbb{R}^n)$ stands for the projection of $\mathbb{R}^n$ onto the subset generated by the components of $x$ indexed by $\mathscr{K}$, $\mathbin{\mathtt{row}}(Y,p)$ is the $p$-th row of $Y$ and $\mathbf{C}$ stands for the subset of $\mathbb{R}^n$ generated by the vector having components zero but those corresponding to the indices defined in $\mathscr{K}$.

\mypara The set $\Xi$ defines the topology of the differential feedback law to be designed for system~\eqref{eq:general system:differential} and the dependence of each element of the matrix $Y$ on the state-space variables. Note that, whenever system \eqref{eq:general system} is linear, the map $Y_{pq}$ is constant.

\begin{theorem}\label{thm:main result}
	If there exists a sum-separable control-contraction metric for system \eqref{eq:general system}, then there exists a solution to Problem~\ref{problem formulation}. In particular, given a graph $\mathscr{G}_c$ describing the communication network among different controllers
\end{theorem}

@@

\mypara In the ``neighbor'' case, the constraint imposed on the matrix $Y$ was that each line of this matrix should depend on the system $i$ and on its neighbors. The the set $\mathscr{K}$ is defined, for each index $i=2,3$, as $\mathscr{K}(i)=\{i-1,i,i+1\}$, $\mathscr{K}(1)=\{1,2\}$ and $\mathscr{K}(4)=\{3,4\}$. The sets $\mathbf{C}$ are defined as
\begin{equation*}
	\begin{array}{rcl}
		\mathbf{C}(1)&=&\{\begin{bmatrix}
		1,&1,&1,&1,&0,&0,&0,&0\end{bmatrix}\},\\
		\mathbf{C}(2)&=&\{\begin{bmatrix}
		1,&1,&1,&1,&1,&1,&0,&0\end{bmatrix}\},\\
		\mathbf{C}(3)&=&\{\begin{bmatrix}
		0,&0,&1,&1,&1,&1,&1,&1\end{bmatrix}\},\\
		\mathbf{C}(4)&=&\{\begin{bmatrix}
		0,&0,&0,&0,&1,&1,&1,&1\end{bmatrix}\}\;.
	\end{array} 
\end{equation*}

\mypara The sets $\mathbin{\mathtt{proj}}_{\mathscr{K}}(\mathbb{R}^8)$ are defined, for each index $i\in\mathbb{N}_{[1,4]}$, as
\begin{equation*}
	\begin{array}{rcl}
		\mathbin{\mathtt{proj}}_{\mathscr{K}(1)}(\mathbb{R}^8)&=&\{\begin{bmatrix}
		q_1,&q_2\end{bmatrix}\}\;,\\
		\mathbin{\mathtt{proj}}_{\mathscr{K}(2)}(\mathbb{R}^8)&=&\{\begin{bmatrix}
		q_1,&q_2,&q_3\end{bmatrix}\}\;,\\
		\mathbin{\mathtt{proj}}_{\mathscr{K}(3)}(\mathbb{R}^8)&=&\{\begin{bmatrix}
		q_2,&q_3,&q_4\end{bmatrix}\}\;,\\
		\mathbin{\mathtt{proj}}_{\mathscr{K}(4)}(\mathbb{R}^8)&=&\{\begin{bmatrix}
		q_3,&q_4\end{bmatrix}\}\;.
	\end{array}
\end{equation*}

\mypara The time taken by the parser to solve the MI \eqref{eq:MI formulation}, in this case, was 3.5 seconds. The matrix $W$ is given by
\begin{equation*}
		W=\mathbin{\mathtt{diag}}(2,1,1,1,1,1,2,1)
\end{equation*}
and the matrix $Y$ has the structure defined, over $q\in\mathbb{R}^8$ as
\begin{equation}\label{eq:example:Y:neighbor and decentralized}
	 Y(q)=\begin{bmatrix}
 	\overline{Y}_1(\cdot)&0&0&0\\
 	0&\overline{Y}_2(\cdot)&0&0\\
 	0&0&\overline{Y}_3(\cdot)&0\\
 	0&0&0&\overline{Y}_4(\cdot)
 \end{bmatrix}\;,
\end{equation}
with elements given, for every $(q_i,\breve{q}_i)\in\mathbb{R}^2\times\mathbb{R}^{\breve{n}_i}$, by 
\begin{equation*}
	\overline{Y}_i(q_i,\breve{q}_i)=-2\begin{bmatrix}
	y_i,&1+\sum_{j\in\mathscr{N}(i)}x_j^2+y_j^2)\end{bmatrix}\;.
\end{equation*}

\mypara In the last case, the fully decentralized scenario has been considered. The time taken by the parser to solve the MI~\eqref{eq:MI formulation} was 2.6 seconds. In this case, for each index $i\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(i)=\{i\}$, $\mathbin{\mathtt{proj}}_{\mathscr{K}(i)}(\mathbb{R}^8)=\{q_i\}$. Moreover, the sets $\mathbf{C}$ are defined as
\begin{equation*}
	\begin{array}{rcl}
		\mathbf{C}(1)&=&\{\begin{bmatrix}
		1,&1,&0,&0,&0,&0,&0,&0\end{bmatrix}\},\\
		\mathbf{C}(2)&=&\{\begin{bmatrix}
		0,&0,&1,&1,&0,&0,&0,&0\end{bmatrix}\},\\
		\mathbf{C}(3)&=&\{\begin{bmatrix}
		0,&0,&0,&0,&1,&1,&0,&0\end{bmatrix}\},\\
		\mathbf{C}(4)&=&\{\begin{bmatrix}
		0,&0,&0,&0,&0,&0,&1,&1\end{bmatrix}\}\;.
	\end{array} 
\end{equation*}
Solving the MI \eqref{eq:MI formulation} the matrix $W$ 
\begin{equation*}
 W=\mathbin{\mathtt{diag}}\left(2,1,1,1,1,1,1,1\right),\\
\end{equation*}
and the matrix $Y$ with structure given by \eqref{eq:example:Y:neighbor and decentralized} with elements defined, for every $q_i\in\mathbb{R}^2$, by 
\begin{align*}
 \overline{Y}_i(q_i)=-\begin{bmatrix}2y_i,3+2(x_i^2+y_i^2)\end{bmatrix}
\end{align*}

@@

\mypara In the unconstrained case, the solver took 9.8s to solve the MI~\eqref{eq:MI formulation} using chordal graphs. The matrix $W$ is given by $\mathbin{\mathtt{diag}}(\overline{W},\overline{W},\overline{W},\overline{W})$, where $\overline{W}=\mathbin{\mathtt{diag}}(0.69,1.24)$. The matrix $Y$ is given by
\begin{equation*}
	Y(q)=\begin{bmatrix}
	\overline{Y}_1(q)&0_{2\times1}&0_{2\times1}&0_{2\times1}\\
	0_{2\times1}&\overline{Y}_2(q)&0_{2\times1}&0_{2\times1}\\
	0_{2\times1}&0_{2\times1}&\overline{Y}_3(q)&0_{2\times1}\\
	0_{2\times1}&0_{2\times1}&0_{2\times1}&\overline{Y}_4(q)
	\end{bmatrix}\;,
\end{equation*}
where $\overline{Y}_i(q)=-\begin{bmatrix}2.38y_i,&2.88+\sum_{j=1}^4(x_j^2+y_j^2)\end{bmatrix}$.

\mypara Using ADMM to compute a solution to the MI~\eqref{eq:Artstein-Sontag:inequality:dual}, the solver took 96[s] and the obtained matrix $W$ has the components shown in

\begin{figure*}
	\begin{subequations}
	\begin{equation}\label{eq:}
		\resizebox{.9\textwidth}{!}{$W_1(q_1)=1\times10^{-5}\begin{bmatrix}
		4+3x_1-1\times10^3y_1+1\times10^{5}y_1^2+5x_1^2-1\times10^{3}x_1y_1&2+6x_1-5\times10^2y_1-6\times10^{2}y_1^2+3x_1^2-8\times10^{2}x_1y_1\\
		*&2+4x_1+3y_1+3y_1^2+5x_1^2+8x_1y_1
		\end{bmatrix}\;,$}
	\end{equation}
	\begin{equation}\label{eq:}
		\resizebox{.9\textwidth}{!}{$W_2(q_2)=1\times10^{-5}\begin{bmatrix}
		5+9x_2-2\times10^3y_2+1\times10^{5}y_2^2+4x_2^2-1\times10^{3}x_2y_2&6+11x_2-1\times10^{3}y_2-7\times10^{2}y_2^2+5x_2^2-9\times10^{2}x_2y_2\\
		*&7+12x_2+10y_2+4y_1^2+6x_1^2+9x_2y_2
		\end{bmatrix}\;,$}
	\end{equation}
	\begin{equation}\label{eq:}
		\resizebox{.9\textwidth}{!}{$W_3(q_3)=1\times10^{-5}\begin{bmatrix}
		7+16x_3-2\times10^3y_3+1\times10^{5}y_3^2+12x_3^2-2\times10^{3}x_3y_3&10+20x_3-1\times10^{3}y_3+1\times10^{3}y_3^2+11x_1^2-11\times10^{3}x_3y_3\\
		*&20+29x_3+29y_3+13y_3^2+13x_3^2+24x_3y_3
		\end{bmatrix}\;,$}
	\end{equation}
	\begin{equation}\label{eq:}
		\resizebox{.9\textwidth}{!}{$W_4(q_4)=1\times10^{-5}\begin{bmatrix}
		11+17x_4-2\times10^3y_4+1\times10^{5}y_4^2+9x_4^2-2\times10^{3}x_4y_4&13+21x_4-1\times10^{3}y_4+1\times10^{3}y_4^2+10x_4^2-1\times10^{3}x_4y_4\\
		*&20+27x_4+24y_4+11y_4^2+12x_4^2+18x_4y_4
		\end{bmatrix}\;,$}
	\end{equation}
	\end{subequations}
\end{figure*}
